The abundance of Bullet Groups in $\Lambda$CDM

### 2014-03-08 paper/ms.tex
updating separation values
abstract

We estimate the expected distribution of displacements between the two
dominant dark matter peaks in halos within a mass range corresponding
to galaxy groups. We find that 5\% to 25\% of the dark matter systems
with circular velocities in the range $300\kms$ to $700\kms$ show
multimodal morphologies with displacements between the dark matter
clumps equal or larger to $\sim 400$\hkpc, which corresponds to the
observational constraint the object SL2S J08544-0121 located at
$z=0.35$. 
\end{abstract}

>>>>

We estimate the expected distribution of displacements between the two
dominant dark matter peaks in halos within a mass range corresponding
to galaxy groups. We find that 50\% to 60\% of the dark matter systems
with circular velocities in the range $300\kms$ to $700\kms$ show
multimodal morphologies with displacements between the dark matter
clumps equal or larger than $133\pm21$\hkpc, which corresponds to the
observational constraint the object SL2S J08544-0121 located at
$z=0.35$. Using the same data we estimate the DM-baryon separation and
find that that $0.1\%$ to $1.0\%$ of the same systems should present
separations equal or larger than $87\pm 14$\hkpc corresponding to the
same observational benchmark.

$133\pm21$\hkpc DM-DM separation
$87 \pm 14$\hkpc DM-baryon separation.

\end{abstract}
